MacLeish

### 2016-05-07 README.Rmd
added picture and updated README

The Ada and Archibald MacLeish Field Station is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation. Reid Bertone-Johnson serves as the Field Station Manager and five faculty and staff sit on the field station's Advisory Board.  More information can be found at (http://www.smith.edu/ceeds/macleish.php)

This R package allows you to download and process weather data (as a time series) using the [ETL](http://www.github.com/beanumber/etl) framework from the MacLeish Field Station. It also contains shapefiles for contextualizing spatial information.

>>>>

The Ada and Archibald MacLeish Field Station is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation. More information can be found at (http://www.smith.edu/ceeds/macleish.php)

![MacLeish Field Station](inst/extdata/macleish_600px.jpg)

This R package allows you to download and process weather data using the [ETL](http://www.github.com/beanumber/etl) framework from the MacLeish Field Station. It also contains shapefiles for contextualizing spatial information.
